---
title: "testing_functions"
format: html
editor: visual
execute: 
    warning: FALSE
---

```{r}
# install.packages(c("testthat", "devtools", "remotes"))
library(testthat)
library(devtools)
library(remotes)
```

## Write a function

```{r}
mean_range <- function(df) {
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE)
  col_mean_max <- max(col_means)
  col_mean_min <- min(col_means)
  return(c(col_mean_min, col_mean_max))
}

mean_range(mtcars)

mean_range(faithful)
```

## Testing the function

write some unit tests

```{r}
# mean_range() should return a range of 2 so to test:
expect_length(mean_range(mtcars), 2)

# mean_range() should always be numeric
expect_type(mean_range(mtcars), "double")

# mean_range() should return 2 values: 1st value should be smaller than 2nd value
expect_true(mean_range(mtcars)[1] <= mean_range(mtcars)[2])
```

## Sourcing code

You just created a function called name_cart() and stored it in /src/

```{r}
source(here::here("src", "name_cart.R"))

name_cart("pizza", "shark")
```

There's an existing R script called cork_oak_growth.R in the src folder.

```{r}
source(here::here("src", "cork_oak_growth.R"))

height_t2(20, 4, 19)
```

To create documentation to your .R scripts:

-   press anywhere within the function within the .R script

-   Press code in top left corner

-   Then select "Insert Roxygen skeleton"
